---
title: "Take Home Exam CS2023"
author: "Georges"
date: "2023-02-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Grading System
The exam is graded out of **30 points**:

- At least 1 map: **5 points**.
- At least 2 distinct plot types: **8 points**. 
- At least 1 creative visualization of your own imagination: **5 points**.
- An introduction text, main body text analyzing the visualizations (interpreting the visualized data), and a conclusion: **5 points**.
- A navigation menu: **5 points**. 
- Presentation and tidiness: **2 points**.

Here are some examples from last year's students who received full marks:

- [World’s Top Bitcoin Mining Countries](https://rpubs.com/giammo23/top_bitcoin_mining_countries)
- [Financial problems in companies due to COVID-19](https://rpubs.com/Julietagalli/904836)
- [Health Facilities Distribution in Kenya - 2018/2019](https://rpubs.com/pmutua/HealthFacilitiesinKenya)

**Note how those students event cited their sources. That counts towards great presentation.**

## What's Next?
- Play with [RShiny](https://shiny.rstudio.com/):
  - [Shiny Basics](https://shiny.rstudio.com/tutorial/written-tutorial/lesson1/)
  - [Build an App](https://rstudio-education.github.io/shiny-course/)
  - [Keep Learning!](https://shiny.rstudio.com/tutorial/)
- Keep practicing R.
- Learn Python.


# Sample Visualizations
Here are some examples!

## My Leaflet Map

```{r, echo=FALSE, message=FALSE}
# LOAD the leaflet library
library(leaflet)

# LOAD the geojsonio library
library(geojsonio)

# Basic example from https://rstudio.github.io/leaflet/
get_basic_map = function(){
  
  m = leaflet() %>%
    addTiles() %>%  # Add default OpenStreetMap map tiles
    addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
  
  return(m)
}

map = get_basic_map()

map

```

## My Pie Chart!

```{r, echo=FALSE}

# The size of each pie slice.
slices = c(10, 12, 4, 16, 8)

# The label for each slice.
labels = c("US", "UK", "Australia", "Germany", "France")

# Invoke the PIE function to draw the pie chart.
# Precede with dev.new() to draw the plot in a new window. 
pie(slices, labels=labels, main="Pie Chart of Countries")

```


## My Map!
This is my map, *check it out*:

```{r, echo=FALSE, message=FALSE}
# LOAD the rworldmap LIBRARY.
library(rworldmap)

# INVOKE the getMap FUNCTION with the resolution ARGUMENT set to "low".
# ASSIGN the map RETURNED by the getMap FUNTION to the my_map VARIABLE.
my_map = getMap(resolution="low")

# ASSIGN the NUMERIC values -73.9 and 40.7 to the NY_lon and NY_lat VARIABLES.
# Thees values represent longitude and latitude coordinate location of New York City
NY_lon = -73.9
NY_lat = 40.7

# Create coordinate VARIABLES for Turin.
Turin_lon = 7.7
Turin_lat = 45.1

# Create coordinate VARIABLES for Reykjavík.
Reyk_lon = -21.82
Reyk_lat = 64.12

#' A FUNCTION that will draw a point and label on the map
#'
#' @param lon the longitude coordinate of the point location.
#' @param lat the latitude coordinate of the point location.
#' @param label the label of the point location.
#' @param pos the position of the label
#' 
draw_map_point = function(lon, lat, label, pos){
  
  # INOKE the points function to draw a red point on the map at the geographic
  # location of the given coordinate
  points(lon, lat, pch=18, col="red")
  
  # INVOKE the text function to draw the names of the place next to its points.
  text(lon, lat, label, pos=pos, col="red", cex=1)
}

# Define the map's boundaries.
boundary_padding = 16
boundary_lon = c(NY_lon-boundary_padding, Turin_lon+boundary_padding)
boundary_lat = c(NY_lat-boundary_padding, Turin_lat+boundary_padding)

# INVOKE the plot FUNCTION to draw the map.
# Set the map boundaries with the xlim and ylim FUNCTION ARGUMENTS.
plot(my_map, xlim=boundary_lon, ylim=boundary_lat)

# INVOKE the draw_map_point function to draw location points and labels.
draw_map_point(NY_lon, NY_lat, "New York", 2)
draw_map_point(Turin_lon, Turin_lat, "Turin", 4)
draw_map_point(Reyk_lon, Reyk_lat, "Reykjavík", 4)

# INVOKE the segments function to draw lines between the city points.
segments(NY_lon, NY_lat, Reyk_lon, Reyk_lat, col="red")
segments(Reyk_lon, Reyk_lat, Turin_lon, Turin_lat, col="red")

```